Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-25 table_fpp.tex
re-ran fpp calculation

\begin{deluxetable*}{lcllllllc}

@@

\label{Tab:FPP}

@@

@@

$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.00074$ & $0.0001$ & $0.22$ & $0.00084$ & Planet \\
 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.011$  & \color{red}  $0.99$  & \color{red}  $0.22$  & \color{red}  $1$  & \color{red}  FP\\
$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.0001$ & $0.15$ & $0.00011$ & Planet \\
$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.004$ & $0.00059$ & $0.17$ & $0.0046$ & Planet \\
$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.00077$ & $< 10^{-4}$ & $0.17$ & $0.00077$ & Planet \\
$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.0013$ & $< 10^{-4}$ & $0.18$ & $0.0013$ & Planet \\
$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00021$ & $0.21$ & $0.00023$ & Planet \\
$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.0026$ & $0.022$ & $0.17$ & $0.025$ & Candidate \\
$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00098$ & $0.13$ & $0.001$ & Planet \\
$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.0018$ & $0.049$ & $0.22$ & $0.051$ & Candidate \\
$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.034$ & $0.055$ & $0.18$ & $0.089$ & Candidate \\
$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.021$ & $0.003$ & $0.14$ & $0.025$ & Candidate \\
 \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.02$  & \color{red}  $0.97$  & \color{red}  $0.18$  & \color{red}  $0.99$  & \color{red}  FP\\
$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0003$ & $0.00012$ & $0.07$ & $0.00042$ & Planet \\
$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet \\
$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0017$ & $0.00065$ & $0.20$ & $0.0024$ & Planet \\
$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.00058$ & $0.00037$ & $0.20$ & $0.00095$ & Planet \\
 \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0027$  & \color{red}  $0.027$  & \color{red}  $0.93$  & \color{red}  $0.07$  & \color{red}  $0.96$  & \color{red}  FP\\
$201569483$ & $1$ & $2.06$ & $0.47$ & $< 10^{-4}$ & $0.092$ & $0.01$ & $0.56$ & Candidate \\
$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.0001$ & $0.20$ & $0.00011$ & Planet \\
$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.0013$ & $0.0021$ & $0.17$ & $0.0034$ & Planet \\
$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.15$ & $< 10^{-4}$ & Planet \\
$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.016$ & $0.0017$ & $0.16$ & $0.018$ & Candidate \\
$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.00063$ & $0.0011$ & $0.17$ & $0.0017$ & Planet \\
$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.0075$ & $0.069$ & $0.09$ & $0.076$ & Candidate \\
 \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.82$  & \color{red}  $0.00022$  & \color{red}  $0.12$  & \color{red}  $0.01$  & \color{red}  $0.94$  & \color{red}  FP\\
$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.004$ & $0.28$ & $0.06$ & $0.28$ & Candidate \\
$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.00019$ & $0.00085$ & $0.22$ & $0.001$ & Planet \\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.0019$ & $0.0015$ & $0.18$ & $0.0034$ & Planet \\
$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0013$ & $0.00064$ & $0.17$ & $0.0019$ & Planet \\
$201779067$ & $1$ & $1.97$ & $0.036$ & $0.005$ & $0.29$ & $0.03$ & $0.33$ & Candidate \\
$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.0017$ & $0.0022$ & $0.17$ & $0.0039$ & Planet \\
$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $0.00017$ & Planet \\
$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet \\
$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.0068$ & $0.052$ & $0.05$ & $0.059$ & Candidate

>>>>

\begin{deluxetable*}{lclccccccc}

@@

\label{Table:FPP}

@@

\colhead{AO?} &

@@

$201208431$ & $1$ & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-4}$ & $0.21$ & $2.2\times10^{-4}$ & Planet \\
 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $0.946$  & \color{red}  $0.054$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.22$  & \color{red}  $1.000$  & \color{red}  FP\\
$201295312$ & $1$ & $0.04$ &  Y & $0.018$ & $6.2\times10^{-4}$ & $< 10^{-4}$ & $0.18$ & $0.019$ & Candidate \\
$201338508$ & $1$ & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.3\times10^{-3}$ & $0.19$ & $1.4\times10^{-3}$ & Planet \\
$201338508$ & $2$ & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.19$ & $1.6\times10^{-4}$ & Planet \\
$201367065$ & $1$ & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.19$ & $< 10^{-4}$ & Planet \\
$201367065$ & $2$ & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.14$ & $< 10^{-4}$ & Planet \\
$201384232$ & $1$ & $0.44$ &  - & $7.7\times10^{-3}$ & $1.5\times10^{-4}$ & $< 10^{-4}$ & $0.20$ & $7.9\times10^{-3}$ & Planet \\
$201393098$ & $1$ & $0.52$ &  - & $0.051$ & $0.011$ & $< 10^{-4}$ & $0.22$ & $0.062$ & Candidate \\
$201403446$ & $1$ & $0.18$ &  Y & $2.3\times10^{-4}$ & $5.6\times10^{-4}$ & $< 10^{-4}$ & $0.17$ & $8.0\times10^{-4}$ & Planet \\
$201445392$ & $1$ & $0.26$ &  - & $0.065$ & $7.4\times10^{-3}$ & $1.9\times10^{-3}$ & $0.20$ & $0.074$ & Candidate \\
$201445392$ & $2$ & $0.18$ &  - & $0.075$ & $8.6\times10^{-3}$ & $0.037$ & $0.22$ & $0.120$ & Candidate \\
$201465501$ & $1$ & $0.68$ &  - & $< 10^{-4}$ & $0.013$ & $8.0\times10^{-4}$ & $0.14$ & $0.014$ & Candidate \\
$201505350$ & $1$ & $2.69$ &  - & $0.642$ & $0.195$ & $1.5\times10^{-3}$ & $0.10$ & $0.839$ & Candidate \\
$201505350$ & $2$ & $0.70$ &  - & $0.012$ & $1.8\times10^{-3}$ & $< 10^{-4}$ & $0.05$ & $0.014$ & Candidate \\
$201546283$ & $1$ & $0.15$ &  - & $6.6\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.08$ & $7.5\times10^{-4}$ & Planet \\
$201549860$ & $1$ & $0.18$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $9.1\times10^{-4}$ & $0.22$ & $9.3\times10^{-4}$ & Planet \\
$201555883$ & $1$ & $0.94$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.0\times10^{-4}$ & $0.15$ & $6.0\times10^{-4}$ & Planet \\
 \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}   -  & \color{red}  $0.843$  & \color{red}  $0.122$  & \color{red}  $0.013$  & \color{red}  $0.05$  & \color{red}  $0.977$  & \color{red}  FP\\
 \color{red} $201569483$  & \color{red}  $1$  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.966$  & \color{red}  $0.023$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.989$  & \color{red}  FP\\
$201577035$ & $1$ & $0.14$ &  Y & $2.9\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.12$ & $3.0\times10^{-3}$ & Planet \\
$201596316$ & $1$ & $0.45$ &  - & $7.6\times10^{-3}$ & $8.2\times10^{-4}$ & $1.3\times10^{-4}$ & $0.20$ & $8.6\times10^{-3}$ & Planet \\
$201613023$ & $1$ & $0.08$ &  Y & $3.3\times10^{-3}$ & $1.2\times10^{-4}$ & $< 10^{-4}$ & $0.22$ & $3.4\times10^{-3}$ & Planet \\
$201617985$ & $1$ & $0.27$ &  - & $< 10^{-4}$ & $1.2\times10^{-4}$ & $8.8\times10^{-3}$ & $0.18$ & $9.0\times10^{-3}$ & Planet \\
$201629650$ & $1$ & $0.43$ &  - & $0.010$ & $9.5\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $0.011$ & Candidate \\
$201635569$ & $1$ & $0.79$ &  - & $3.9\times10^{-4}$ & $0.018$ & $0.037$ & $0.08$ & $0.055$ & Candidate \\
 \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.971$  & \color{red}  $0.018$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.989$  & \color{red}  FP\\
$201702477$ & $1$ & $0.70$ &  - & $0.445$ & $0.051$ & $5.6\times10^{-4}$ & $0.05$ & $0.497$ & Candidate \\
$201736247$ & $1$ & $0.42$ &  - & $5.5\times10^{-3}$ & $3.8\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $5.9\times10^{-3}$ & Planet \\
$201754305$ & $1$ & $0.65$ &  - & $7.3\times10^{-3}$ & $2.7\times10^{-4}$ & $2.5\times10^{-4}$ & $0.20$ & $7.9\times10^{-3}$ & Planet \\
$201754305$ & $2$ & $0.38$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.6\times10^{-4}$ & $0.20$ & $3.3\times10^{-4}$ & Planet \\
 \color{red} $201779067$  & \color{red}  $1$  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.971$  & \color{red}  $0.017$  & \color{red}  $2.5\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.988$  & \color{red}  FP\\
$201828749$ & $1$ & $0.39$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $3.5\times10^{-4}$ & $0.17$ & $3.5\times10^{-4}$ & Planet \\
$201855371$ & $1$ & $0.62$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\
$201912552$ & $1$ & $0.47$ &  Y & $0.023$ & $2.4\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $0.023$ & Candidate \\
$201929294$ & $1$ & $3.12$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet
